---
title: "Lab 10"
author: "Julia Wilson"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Attach Packages
library(tidyverse)
library(here)
library(janitor)
library(sf)
library(beepr)
library(praise)
library(cowsay)
library(usethis)
library(paletteer)
```

## beepr::beep()

Use `beep()` to give yourself an audio alert

## For loop + beep 

Notes: 
Don't see for loops a lot bc there are functions that do this for you, so you don't have to write for loops. We are going to create 99 bottles of beer on the wall. We will create a sequence from 1 to 99 and then reverse it. 

rev(seq(1:99))

rev: is a reverse function

i = element 

paste these different pieces together into a string: print(past(i, ""))


```{r, eval = FALSE}
for (i in rev(seq(1:99))) {
  print(paste(i, "bottles of beer on the wall"))
} 

beep(4)
```

## Praise is nice

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```

## cowsay::say to have characters say something 

```{r}
say("I love tacos!", by = "shark")
say("Hi Evie", "egret", by_color = "cyan", what_color = "pink")
```

## usethis for everything

updating R profile :) 

R Project first, then git & GitHub repo:  

- usethis::use_git()
- usethis::use_github()

It will automatically send you to github where you can branch, rename, and then copy and paste the code it supplies. Paste the code into terminal. Refresh your Git sections and the arrows for pull/push should be lit up now. 

## paletter: aggregated color palettes 












